External Patch Group Prior Guided Internal Orthogonal Dictionary Learning for Real Image Denoising

### 2016-10-23 CVPR2017_Review_Unified.tex
ad

The above mentioned methods can be categorized into external methods which learn priors from external images to recover noisy images, and internal ones which exploit priors of given images for denoising. The external priors in natural images are free of the high correlation between noise and siganls in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image. Combining the priors of external clean images and adaptivety of internal testing images can naturally improve the performance of denoising methods, especially on real noisy images. Based on these observations, in this paper, we propose to employ the external patch group prior \cite{pgpd} of natural clean images to guide the clustering of internal patch groups in given noisy image, and develop an external prior guided internal orthogonal dictionary learning (DL) algorithm for real image denoising. The internal orthogonal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary. Both of the two stages have closed-form solutions. Hence, our internal DL process is very efficient for online internal denoising.

% In fact, the external PG prior learning based model is employed to guide the clustering of internal PGs extracted from the input noisy images. Then for each cluster of PGs, we perform subspace learning by PCA and denoising by weighted sparse coding. We perform comprehensive experiments on real noisy images captured by different CMOS or CCS sensors. The results demonstrate that our method achieves comparable or even better performance on denoising real noisy images. An initial glimpse of our method is also listed in Figure \ref{fig1}. This reveals the potential advantages of combining external and internal information o natural images on robust and complex real noisy image denoising problem.

\subsection{Our Contributions}
The contributions of this paper are summarized as follows:
\begin{itemize}
\item We propose a noval method which combine the external and internal PG prior for real noisy image denoising problem;
\item Our method doesn't need noise modeling and estimation, and the noise levels of real noisy images are automatically expresssed by the singular values of learned subspace;
\item We achieve much better performance on visual quality, PSNR, SSIM, and speed, than other competing methods for real image denoising problem.
\end{itemize}

The rest of this paper will be summerized as follows: in Section 2, we will introduce the related work close to our work; in Section 3, we will introduce our proposed external prior guided internal subspace learning framework for real image denoising; in Section 4, we will demonstrate the denoising experiments on several standard dataset; in Section 5, we will conclude our paper and give our future work.

>>>>

The above mentioned methods can be categorized into external methods which learn priors from external images to recover noisy images, and internal ones which exploit priors of given images for denoising. The external priors in natural images are free of the high correlation between noise and siganls in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image. Combining the priors of external clean images and adaptivety of internal testing images can naturally improve the performance of denoising methods, especially on real noisy images. Based on these observations, in this paper, we propose to employ the external patch group prior \cite{pgpd} of natural clean images to guide the clustering of internal patch groups in given noisy image, and develop an external prior guided internal orthogonal dictionary learning (DL) algorithm for real image denoising. The internal orthogonal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary. Both of the two stages have closed-form solutions. Hence, our internal DL process is very efficient for online internal denoising. Through comprehensive experiments on real noisy images captured by different cameras and settings, we demonstrate that the proposed method achieves better performance on real image denoising

\subsection{Our Contributions}
The contributions of this paper are summarized as follows:
\begin{itemize}
\item We propose a noval dictionary learning method which employ the external prior guided the internal orthogonal dictionary learning for real image denoising. Both the external prior and internal prior are performed on patch groups instead of patches.
\item The internal orthogonal dictionary learning are alternating iterative solved with closed-form solutions. The learned orthogonal dictionary are very efficient in both learning and denoising stages. 
\item We achieve much better performance on the real image denoising problem than other competing methods in terms of visual quality, PSNR, and SSIM.
\end{itemize}

The rest of this paper will be summerized as follows: in Section 2, we will introduce the related work; in Section 3, we will introduce the proposed external prior guided internal orthogonal dictionary learning algorithm for real image denoising; in Section 4, we will demonstrate the extensive experiments on two standard dataset; we will conclude our paper and give our future work in Section 5.
